Msc Thesis Figures

### 2021-03-29 docs/msc_thesis_figures.Rmd
cahneg legend to reflect no baseline

```{r figure_1_model_1, message=FALSE,  warning=FALSE, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100"}
colors_sce <- 
  data.frame(sce = c("Hist", "Baseline", "RCP85"), 
             color = c("#8DA0CB", "#FC4E2A", "#800026"), stringsAsFactors = F)

fig_1_static_chap_1 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_1")) %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values = colors_sce$color, 
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  #geom_point(aes(group = sce)) +
  scale_linetype_manual(values=c("solid", "twodash")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  #geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=1, override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0.85, 0.15))+
  NULL
#fig_1_static_chap_1
ggsave(fig_1_static_chap_1, 
       filename = "../thesis/figures/connectivity_decrease_x5species_chap1.png", 
       width = the_width, height = the_height, dpi = the_dpi)
```

@@

```{r figure_1_model_2, message=FALSE, warning=FALSE, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100"}
fig_1_static_chap_2 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_2")) %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values = colors_sce$color,
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  scale_linetype_manual(values=c("solid", "dashed", "longdash", "dotted")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow = 2, ncol=2, 
                                 override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0.85, 0.15))+
  NULL
#fig_1_static_chap_2
ggsave(fig_1_static_chap_2, 
       filename = "../thesis/figures/connectivity_decrease_x5species_chap2.png", 
       width = the_width, height = the_height, dpi = the_dpi)
```

@@

```{r surf_1, message=FALSE, warning=FALSE, out.width="100%"}
surf_1 <- surf %>% 
  mutate(scenario = as.factor(scenario)) %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_1")) %>% 
  filter(climate != "none") %>% 
  group_by(scenario, species, iter) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$kp_nb, 
                       the_diff = ((kp_nb-baseline)/baseline)*100 )) %>% ungroup %>% 
  ggplot(aes(x = timestep, y = the_diff, color=climate)) +
  scale_linetype_manual(values=c("solid", "twodash")) +
  geom_smooth(aes(group = scenario, linetype=code_run), alpha=0.2, method="loess")+
  #geom_point(aes(group=scenario), alpha= 0.05, size = 0.5)+
  facet_wrap(~species, scales = "fixed")+
  scale_color_manual(values = colors_sce$color,
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  labs(y = "Change in nb of Keypoints detected (%)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=1, override.aes = list(colour = 'black'))) +
  NULL
#surf_1
ggsave("../thesis/figures/surf_chap1.png", surf_1,
       width = the_width, height = the_height, dpi = the_dpi)
```

@@

```{r surf_2, message=FALSE, warning=FALSE, out.width="100%"}
surf_2 <- surf %>% 
  mutate(scenario = as.factor(scenario)) %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_2")) %>% 
  filter(climate != "none") %>% 
  group_by(scenario, species, iter) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$kp_nb, 
                       the_diff = ((kp_nb-baseline)/baseline)*100 )) %>% ungroup %>% 
  ggplot(aes(x = timestep, y = the_diff, color=climate)) +
  geom_smooth(aes(group = scenario, linetype=code_run), alpha=0.2, method="loess")+
  #geom_point(aes(group=scenario), alpha= 0.05, size = 0.5)+
  scale_linetype_manual(values=c("solid", "dashed", "longdash", "dotted")) +
  facet_wrap(~species, scales = "fixed")+
  scale_color_manual(values = colors_sce$color,
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  labs(y = "Change in nb of Keypoints detected (%)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=2, ncol=2, 
                                 override.aes = list(colour = 'black'))) +
  NULL
#surf_2
ggsave("../thesis/figures/surf_chap2.png", surf_2,
       width = the_width, height = the_height, dpi = the_dpi)
```

>>>>

```{r figure_1_model_1, message=FALSE,  warning=FALSE, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100"}
colors_sce <- 
  data.frame(sce = c("Hist", "RCP85"), 
             color = c("#8DA0CB", "#800026"), stringsAsFactors = F)

fig_1_static_chap_1 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_1")) %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values = colors_sce$color, 
                     labels = colors_sce$sce) +
  geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  #geom_point(aes(group = sce)) +
  scale_linetype_manual(values=c("solid", "twodash")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  #geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=1, override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0.85, 0.15))+
  NULL
#fig_1_static_chap_1
ggsave(fig_1_static_chap_1, 
       filename = "../thesis/figures/connectivity_decrease_x5species_chap1.png", 
       width = the_width, height = the_height, dpi = the_dpi)
```

@@

```{r figure_1_model_2, message=FALSE, warning=FALSE, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100"}
fig_1_static_chap_2 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_2")) %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values = colors_sce$color,
                     labels = colors_sce$sce) +
  geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  scale_linetype_manual(values=c("solid", "dashed", "longdash", "dotted")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow = 2, ncol=2, 
                                 override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0.85, 0.15))+
  NULL
#fig_1_static_chap_2
ggsave(fig_1_static_chap_2, 
       filename = "../thesis/figures/connectivity_decrease_x5species_chap2.png", 
       width = the_width, height = the_height, dpi = the_dpi)
```

@@

```{r surf_1, message=FALSE, warning=FALSE, out.width="100%"}
surf_1 <- surf %>% 
  mutate(scenario = as.factor(scenario)) %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_1")) %>% 
  filter(climate != "none") %>% 
  group_by(scenario, species, iter) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$kp_nb, 
                       the_diff = ((kp_nb-baseline)/baseline)*100 )) %>% ungroup %>% 
  ggplot(aes(x = timestep, y = the_diff, color=climate)) +
  scale_linetype_manual(values=c("solid", "twodash")) +
  geom_smooth(aes(group = scenario, linetype=code_run), alpha=0.2, method="loess")+
  #geom_point(aes(group=scenario), alpha= 0.05, size = 0.5)+
  facet_wrap(~species, scales = "fixed")+
  scale_color_manual(values = colors_sce$color,
                     labels = colors_sce$sce) +
  labs(y = "Change in nb of Keypoints detected (%)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=1, override.aes = list(colour = 'black'))) +
  NULL
#surf_1
ggsave("../thesis/figures/surf_chap1.png", surf_1,
       width = the_width, height = the_height, dpi = the_dpi)
```

@@

```{r surf_2, message=FALSE, warning=FALSE, out.width="100%"}
surf_2 <- surf %>% 
  mutate(scenario = as.factor(scenario)) %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_2")) %>% 
  filter(climate != "none") %>% 
  group_by(scenario, species, iter) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$kp_nb, 
                       the_diff = ((kp_nb-baseline)/baseline)*100 )) %>% ungroup %>% 
  ggplot(aes(x = timestep, y = the_diff, color=climate)) +
  geom_smooth(aes(group = scenario, linetype=code_run), alpha=0.2, method="loess")+
  #geom_point(aes(group=scenario), alpha= 0.05, size = 0.5)+
  scale_linetype_manual(values=c("solid", "dashed", "longdash", "dotted")) +
  facet_wrap(~species, scales = "fixed")+
  scale_color_manual(values = colors_sce$color,
                     labels = colors_sce$sce) +
  labs(y = "Change in nb of Keypoints detected (%)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=2, ncol=2, 
                                 override.aes = list(colour = 'black'))) +
  NULL
#surf_2
ggsave("../thesis/figures/surf_chap2.png", surf_2,
       width = the_width, height = the_height, dpi = the_dpi)
```
